ICM testing

### 2023-04-27 Scripts/ASR_stocks.Rmd
Building the north sea multi-species model
And other updates.

  tst <- back.sim(years,
                 mat.age = age.mat,
                 nm = prop.nat.mort,
                 w.age = weight.age,
                 ages = ages,
                 rems = rem$rem,
                 fecund = mx,
                 N.end = N.end,
                 pop.model = 'exponential',
                 n.sims = 2,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)

@@

################# Now run as a forward simulation
  N.start <- vpa.abund[1]

  tst <- for.sim(years,
                 mat.age = age.mat,
                 nm = prop.nat.mort,
                 w.age = weight.age,
                 ages = ages,
                 rems = rem$rem, # rep(0,nrow(rem)),
                 fecund = mx,
                 N.start = N.start,
                 pop.model = 'exponential', K = 2e6,
                 n.sims = 2,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)

  for.res[[i]] <- tst
  for.ts[[i]] <- did.it.work
  for.ts.quants[[i]] <- quants

ggplot(quants) + geom_line(aes(x=years,y=med))

########################## Now run the tuning sims

  N.end <- vpa.abund[length(vpa.abund)]
  tunes <- tune.sim(years,
                    n.steps = 100,
                    abund.ts = vpa.abund,
                    mat.age = age.mat,
                    nm = prop.nat.mort,
                    w.age = weight.age,
                    ages = ages,
                    rems = rem$rem,
                    fecund = mx,
                    N.end = N.end,
                    pop.model = 'exponential')

  tuned.res[[i]] <- tunes
} # end i in Stocks look

>>>>

  tst <- back.sim(years,
                 mat.age = age.mat,
                 nm = prop.nat.mort,
                 w.age = weight.age,
                 ages = ages,
                 rems = rem$rem,
                 fecund = mx,
                 N.end = N.end,
                 pop.model = 'exponential',
                 n.sims = 500,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)

@@

# ################# Now run as a forward simulation
#   N.start <- vpa.abund[1] 
# 
#   tst <- for.sim(years,
#                  mat.age = age.mat,
#                  nm = prop.nat.mort,
#                  w.age = weight.age,
#                  ages = ages,
#                  rems = rem$rem, # rep(0,nrow(rem)),
#                  fecund = mx,
#                  N.start = N.start,
#                  pop.model = 'exponential', K = 2e6,
#                  n.sims = 2,
#                  sd.mat = 0.5,
#                  sd.nm = 0.5,
#                  sd.wt = 0.5,
#                  sd.fecund = 0.5)
# 
#   #Combine the data
#   did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
#   # Here get the Upper and lower 50% quantiles to make a functional boxplot
#   quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
#                                                                         med = median(abund),
#                                                                         U.50 = quantile(abund,probs=c(0.75)))
# 
#   for.res[[i]] <- tst
#   for.ts[[i]] <- did.it.work
#   for.ts.quants[[i]] <- quants

# ########################## Now run the tuning sims
# 
#   N.end <- vpa.abund[length(vpa.abund)]
#   tunes <- tune.sim(years,
#                     n.steps = 100,
#                     abund.ts = vpa.abund,
#                     mat.age = age.mat,
#                     nm = prop.nat.mort,
#                     w.age = weight.age,
#                     ages = ages,
#                     rems = rem$rem,
#                     fecund = mx,
#                     N.end = N.end,
#                     pop.model = 'exponential')
# 
#   tuned.res[[i]] <- tunes
} # end i in Stocks look
#
